Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2020-12-31 2.background/2.RV_and_RS.tex
minor edits
added

1) ?.Example.tex files for each chapter conforming to the current style.

2) Began the "index".  If you want to include a term do \index{term}{term}

3) Fixed the level of the table-of-contents.
Added Remark 2.2
This addresses the fact that ependent maxima of rapidly varying variables cannot grow at a fasster rate than maxima of iid such variables.

>>>>

\stilian{ 
\begin{remark} \label{rem:iid-max} Part (1) of Proposition \ref{prop:rapid-varying-tails} is equivalent to 
\begin{equation}\label{e:rem:iid-max}
  \P\left[\frac{1}{u_p} M_p >  1+\delta_p \right] \longrightarrow 0,\ \ \mbox{ as }p\to\infty,
\end{equation}
for some positive sequence $\delta_p\to 0$.  Notice on the other hand that if $M_p^*$ is the maximum of $p$ iid variables with distribution $F$,
the relative stability property entails $M_p^*/u_p \to 1$, in probability, as $p\to\infty$.  Since the sequence $1+\delta_p\to 1$, 
Relation \eqref{e:rem:iid-max} means that the rate of growth of the maxima $M_n$ in ${\cal E}$ cannot be faster than that of the independent
maxima $M_p^*$.  This somewhat surprising fact is true regardless of the dependence structure of ${\cal E}$ and is solely a 
consequence of the rapid variation of $F$.
\end{remark}
}{}
